Human Capital Model

### 2016-02-01 Tex/paper.tex
laws added
123

\section{Introduction}
\label{sec:introduction}

Considering the shortage of the talent, it's essential for companys to
retain good people and make them well-trained. However, current
situation is not satisfactory while many talents always tend to get a
good job via job-hopping, causing orgnizational churn in employees who
are closely connected to them. In order to simulate this process and
improve it, we build a human capital model based on Social Network
Analysis and Markov process.

\begin{displaymath}
Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
\end{displaymath}

@@

\begin{displaymath}
\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{}
\end{displaymath}

\subsection{Restatement of the Problem}
\label{sec:restatement-of-the-problem}
We are required to build a mathematical model to solve the problem of heating water in bathtub. Thus we have some subproblems:
\begin{itemize}
\item Build a basic model that demonstrate the change of the temperature in the bathtub in space and time without other intervention.
\item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
\item Propose a strategy to keep the temperature as even as possible.
\end{itemize}
In the first step, we build the simplest model. The shape of the bathtub is a cuboid, and the person will stay still. In the second step, the person move slowly and the shape of the bathtub changes. In the third step, we develop the conclusion of the  strategy.
\subsection{Literature Review}
\label{sec:literature-review}

\begin{itemize}
\item
\item
\item
\end{itemize}

\section{Terminology}
\label{sec:terminology}

\begin{itemize}
\item
\item
\item
\end{itemize}

@@

% the main section of the paper
\section{Human Capital Model}
\label{sec:human-capital-model}

@@

Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{l|l}
  Constant & Description \\
  \hline
  $k$            &Thermal conductivity of water \\
  $\rho$         &Density of water \\
  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
  $C_w$          &Specific heat capacity of water \\
  $V$            &Total volume of water \\
  $x_s$          &Humidity ratio in saturated air \\
  $x_0$          &Initial humidity ratio in the air \\
  $A$            &Square of water surface \\
  $V_a$          &Volume of surrounding air \\
  $C_v$          &Evaporation heat of water \\
  $u_2$          &Temperature of person's surface \\

@@

Totally, internal energy of water changes while heat changes.
Then the temperature changes with
\begin{equation}
 1
\end{equation}

Considering the right side of equation 1.
Fourier theorem indicates that,
\begin{equation}
 dQ=-k\frac{\vartheta u}{\vartheta n}dSdt
\end{equation}
holds for the heat flow along a surface with square of dS.
In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$
is the derivative of u along the normal line. Thus, after integration of dQ by time and
space
\begin{equation}
 \Delta Q_1=int_{t_1}^{t_2}[{int_{\Gamma}}k\frac{\vartheta u}{\vartheta n}dS]dt
\end{equation}
The heat flow into the water by thermal conduction could be calculated by this equation.

@@

It is obvious that the excess water is as the same value of hot water in any time period.
Thus $\Delta Q_3$ can be calculated by
$\Delta Q_3={\Delta m}Cu$.
Also, $\Delta m=v{\Delta t}$.

According to thermal theorem, heat loss in vaporization is proportional to
the weight of vapor water.
$\Delta Q_4={C_v}\Delta {m_v}$.

Since water could be considered as manifold, according to Green formula,
\begin{equation}
 2
\end{equation}.

Combining the equations above,
\begin{equation}
 3
\end{equation}.
Some parameters would be discussed in the following sections.

@@

In our model, the initial value condition is the initial temperature of water. We assume the temperature is equilibrium throughout the bathtub.

\subsection{PDE Solve}

@@

\subsection{Analysis for Task 2}
\label{sec:analysis-for-task-2}

a

\subsection{Analysis for Task 3}
\label{sec:analysis-for-task-3}

We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company. With these two assumption, results can be drawn according to our model through simulation.

Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.

\begin{tabular}{*{4}{c}}\toprule[2pt]
Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
\end{tabular}

\subsection{Analysis for Task 4}
\label{sec:analysis-for-task-4}

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_p.pdf}\\
  \caption{Status of positions}\label{t4_p}
\end{figure}

To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints. We execute our program 100 times for each churn rate and average the predicted values. Figure \ref{t4_p} shows the averaged results our model predicted. Under all of these three conditions, the number of employees in the company keeps rising. The higher the churn rate, the lower the final full rate the company reaches after two years. But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_r.pdf}\\
  \caption{Recruiting budget}\label{t4_r}
\end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=7cm]{task4_t.pdf}
  \includegraphics[width=7cm]{task4_s.pdf}\\
  \caption{Training budget and salary budget}\label{t4_t_s}
\end{figure}
The churn rate effect the budget of the company as well. The three parts of the bugdet behave differently when churn rate increases. The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}. Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart. It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.

To maintain enough employees, the company has to spend more on recruiting. So high turnover rate directly increase the recruiting budget. High turnover rate's effect on training budget and salary budget is more complex. On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate. On the other hand, the vacancies in lower level remains low because of the short recruiting time. So the full rate of the company decreases when churn rate rises. Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task5_p.pdf}\\
  \caption{Status of position}\label{t5_p}
\end{figure}
We apply following changes to our model to simulate the required process:\\
\begin{itemize}
\item Change the churn rate of junior managers and experienced supervisors to 30\%
\item Prohit external recruiting
\item Promoting only qualified employees
\end{itemize}
\begin{table}
	\begin{center}
		\begin{tabular}{l|cc}\toprule[2pt]
		\bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
		Senior manager/Executive & 5.6 & 8.4\\
		Junior manager/Executive & 9.0 & 18.4\\
		Experienced supervisor & 7.4 & 23.0\\
		Inexperienced supervisor & 9.2 & 23.2\\
		Experienced employee & 72.6 & 107.4\\
		Inexperienced employee & 99.6 & 149.6\\
		Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
		\end{tabular}
		\caption{Status of position}\label{t5_p_t}
	\end{center}
\end{table}

The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}. All the data shown is an average of ten predictions. While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.

We list specific data of each level in Table \ref{t5_p_t}. In the modified case, the numbers of employees are lower than original case especially the those of middle levels. Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave. Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low. The situation given in that task 5 will cause unrecoverable damage to ICM's HR health. With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.

\section{Advice for HR}
\label{sec:advice-for-hr}

a

\subsection{Incentive Mechanism}
\label{sec:incentive-machanism}

a

\subsection{Matching Employees to the Right Position}
\label{sec:matching-employees-to-the-right-position}

a

\section{Team Science}
\label{sec:team-science}

a

@@

a

@@

\begin{itemize}
\item Our model make fully use of the theory of multilayer networks so
  that it quantizes the relation accurately and reasonablly.
\item Our model exellently proves the interaction among these
  factors:leave probability, promotion probability and productivity.
\item The network we built include both microcosmic part and
  macrocosmic part, and they react to each other.
\item Our model proves the effection of time.
\end{itemize}

@@

\section{Conclusions}
\label{sec:conclusions}

a

>>>>

\section{Introduction}
\label{sec:introduction}
\begin{displaymath}
Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
\end{displaymath}

@@

\begin{displaymath}
\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
\end{displaymath}

\subsection{Restatement of the Problem}
\label{sec:restatement-of-the-problem}
We are required to build a mathematical model to solve the problem of heating water in bathtub. Thus we have some subproblems:
\begin{itemize}
\item Build a basic model that demonstrate the change of the temperature in the bathtub in space and time without other intervention.
\item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
\item Propose a strategy to keep the temperature as even as possible.
\end{itemize}
In the first step, we build the simplest model. The shape of the bathtub is a cuboid, and the person will stay still. In the second step, the person move slowly and the shape of the bathtub changes. In the third step, we develop the conclusion of the  strategy.

@@

% the main section of the paper
\section{Water in the Bathtub Model}
\label{sec:human-capital-model}
Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{l|l}
  Constant & Description \\
  \hline
  $k$            &Thermal conductivity of water \\
  $\rho$         &Density of water \\
  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
  $C_w$          &Specific heat capacity of water \\
  $V$            &Total volume of water \\
  $x_s$          &Humidity ratio in saturated air \\
  $x_0$          &Initial humidity ratio in the air \\
  $A$            &Square of water surface \\
  $V_a$          &Volume of surrounding air \\
  $C_v$          &Evaporation heat of water \\
  $u_2$          &Temperature of person's surface \\

@@

@@

Totally, internal energy of water changes while heat changes.
Then the temperature changes with
\begin{equation}
 Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
\end{equation}
, in which $\Omega$ is the region of water, $\rho$ is the density of water, $u_f$ is the final temperature when t=$t_2$, $u_i$ is the initial temperature when t=$t_1$.

Considering the right side of equation 1.
Fourier theorem indicates that,
\begin{equation}
 dQ=-k\frac{\vartheta u}{\vartheta n}dSdt
\end{equation}
holds for the heat flow through surface with square of dS.
In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
\begin{equation}
 \Delta Q_1=int_{t_1}^{t_2}[{int_{\Gamma}}k\frac{\vartheta u}{\vartheta n}dS]dt
\end{equation}
in which $\Gamma$ is the boundary of $\Omega$.
The heat flow into the water by thermal conduction could be calculated by the equation.

@@

It is obvious that the excess water is as the same value of hot water in any time period.
Thus $\Delta Q_3$ can be calculated by
$\Delta Q_3={\Delta m}{C_w}u$.
Also, $\Delta m=v{\Delta t}$. 
$\Delta v$ is the weight of hot water each second, $\Delta m$ is the weight of hot water in $\Delta t$.

According to thermal theorem, heat loss in vaporization is proportional to
the weight of vapor water.
$\Delta Q_4={C_v}\Delta {m_v}$.
$\Delta {m_v}$ is the weight of evaporation water in $\Delta t$, $\Delta {C_v}$ is evaporation heat of water.

Since water could be considered as manifold, according to Green formula,
\begin{equation}
 \int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
\end{equation}.

Combining the equations above,
\begin{equation}
 \rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
\end{equation}.
In this heat equation, $u_h$ and $v_h$ are two variables that control the strategy.

Now discuss g, evaporation rate per square. According to empirical formula in [], we know that
\begin{equation}
 g=\frac{(25+19v)({x_s}-x)}{3600}
\end{equation}
in which v is the velocity of air, ${x_s}$ is humidity ratio in saturated air, $x$ is humidity ratio in air. 
Considering the water vapor rate in the air, it indicates 
\begin{equation}
 x=x_0+\int \frac{Ag}{\rho V_a}dt
\end{equation}
in which, $x_0$ is the initial humidity ratio in the air, $\rho$ is density of water, $V_a$ is the total air volume of surrounding air.

Combing the two equations and differentiating, we get a ordinary partial equation 
\begin{equation}
 \frac{3600}{25+19v} \frac{dg}{dt}=\frac{A}{\rho {V_a}}
\end{equation}
Solving the equation, we get the solution 
\begin{equation}
 g=\frac{(25+19v)({x_s}-{x_0})}{3600}e^{-\lambda t}, \lambda =\frac{A(25+19v)}{3600\rho {V_a}}
\end{equation}

@@

In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It would take several steps to calculate them.

Consider the temperature of air, $u_1$. Heat change of air consists of two aspects, heat conduction and evaporation.

In our model, we assume the temperature of water is equilibrium throughout the bathtub initially.

\subsection{PDE Solve}
\label{sec:PDE solve}
Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this problem.

We use Partial Differential Equation Toolbox in matlab to solve our equations. Partial Differential Equation Toolbox makes use of finite element method to discrete irregular geometry and calculate a relatively precise solution. get solution of temperature corresponding to different $u_h$ and $v_h$. By comparing temperature distribution, we choose proper parameters as the best strategy.

First, we build a 3D geometry model to simulate a proper-size bathtub, as shown in Figure 2. Matlab divided the geometry into several elements.

Then we input the heat equation and initial-boundary value conditions. Boundary value conditions are different in three parts.

@@

@@

\subsection{Parameters of Bathtub}
\label{sec:parameters of bathtub}
\begin{itemize}
\item
\item
\end{itemize}

\subsection{Parameters of Person}
\label{sec:parameters of person}
\begin{itemize}
\item
\item
\item
\end{itemize}

\subsection{Effects of Motion}
\label{sec:effects of motion}

\subsection{Effects of Bubble Bath Additive}
\label{sec:effects of bubble bath additive}

@@

\begin{itemize}
\item Our model make fully use of the theory of multi-layer networks so
  that it quantizes the relation accurately and reasonably.
\item Our model excellently proves the interaction among these
  factors:leave probability, promotion probability and productivity.
\item The network we built include both microcosmic part and
  macrocosmic part, and they react to each other.
\item Our model proves the effect of time.
\end{itemize}

@@
